A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-07 ms.Rmd
some rubbish discussion coming into shape...

# DISCUSSION
We found a significant effect of phylogenetic signal in our study, which contrasts with previous studies [@evans2011makes]. Niche breadth, as measured by generalism, was significantly associated with our urbanization index across all analyses. Conversely, granivores and insectivores were consistently selected against. Residual brain mass was significantly important within our phylogenetic models, suggesting that within a clade, it is the species with the largest residual brain mass that are most readily observed in urban areas. A similar pattern was found for body size, although not significant. Our results suggests that urbanization selects against specialist species.

@@

We provide the largest study to date using a continuous urbanization metric in order to assess biological and ecological traits which predict a species' adaptability to urban environments. Understanding specific species' traits which are associated with urban birds allows us to fully understand how to best preserve and maintain avian diversity in cities. We recommend that urban areas should focus on providing habitats which allow granivores, insectivores, and others to be found more readily in cities.

>>>>

# DISCUSSION
Our continuous urbanization index showed a significant phylogenetic signal [@revell2008phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence, @ibanez2017global, @sol2017urbanisation, @la2018phylogenetic]. This contrasts with previous studies [@evans2011makes], but is likely a result of sample size considerations. Niche breadth, as measured by generalism, was significantly associated with our urbanization index across both phylogenetic and non-phylogenetic analyses, confirming the notion that urban birds have broad environmental tolerance [@bonier2007urban]. Conversely, granivores and insectivores were consistently selected against. Residual brain mass was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade, the species with the largest residual brain mass are most readily observed in urban areas. A similar pattern was found for body size, although not significant.

Traditionally, the literature which aims to associate avian species' traits with urbanization has been limited, and as such has lead to less generalizable patterns. The majority of studies in this space have focused on discrete classifications of species into adapters, avoiders, and exploiters [e.g., ], or even binary classification based on presence/absence in cities or towns [e.g., ]. We highlight that our analysis used a total of 477 species (Appendix 4), which is greater than many previous studies.

 Our results suggest that urbanization selects against specialist species.

@@

We provide the largest study to date using a continuous urbanization metric in order to assess biological and ecological traits which predict a species' adaptability to urban environments.

Global broad-scale empirical datasets are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global, @aronson2016hierarchical, @gutierrez2018citizen], in large part due to the growing use of citizen science data [@silvertown2009new] in combination with rapidly expanding remote sensing technology [@gorelick2017google].

 is rapidly expanding our understanding of urbanization impacts on birds [e.g., ] Understanding specific species' traits which are associated with urban birds allows us to fully understand how to best preserve and maintain avian diversity in cities. We recommend that urban areas should focus on providing habitats which allow granivores, insectivores, and others to be found more readily in cities.

Our study looked over a broad spatial and temporal scale to identify a novel approach to quantifying a continuous urbanization index for birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role, @lepczyk2017global], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (i.e., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [CITATIONS]. Further, future studies should look to expand this analysis outside of the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales (i.e., does city size affect the patterns found here; [@sol2017urbanisation, @batary2017non]). Future studies should aim to (1) broaden the spatial scale, (2) investigate the temporal changes in a species' urbanization indices [@la2014role, @lepczyk2017global], and (3) investigate the role that city size plays on selected traits and phylogenetic diversity [@sol2017urbanisation, @batary2017non].

Ultimately, we highlight the applicability of broad-scale empirical data to assess species' traits which predict presence and adaptability in urban environments. Our results suggest that generalist species are better prepared to forage and survive in the ecologically novel aspects of urban environments [CITATIONS]. Australia is a relatively young country and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [CITATION]. Furthermore, future studies should focus on broad-scale data to form generalizable patterns which rely on continuous measures for improved modelling performance.
